---
title: "Sachin_Performance"
author: "Abinashi Prakash"
date: "23 June 2019"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Project Overview:
This peer assessed assignment has two parts,

1) need to create a Shiny application which will reflect Sachin's Score against each test playing country and deploy it on Rstudio's servers.

2) use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application.

## Steps to Perform:
1. Create a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server.
3. Share the application link by pasting it into the provided text box.
4. Share server.R and ui.R code on github.

## Application Overview:
Sachin Tendulkar is one of the best player in the history of Cricket.This Application will provide the snapshot of Sachin Tendulkar's score against each test playing country. 
Extracted the "tendulkar.csv" data file from package "cricketr" which is being developed by "Tinniam V Ganesh".Source for this dataset is "http://www.espncricinfo.com/ci/content/stats/index.html".
I have placed,

a) Data file at ("https://raw.githubusercontent.com/abinashi-prakash/ShinyApp/master/tendulkar.csv").
b) The application is running on (https://abinashiprakash.shinyapps.io/Sachin_Score_App/).
c) ui.R, and Server.R Code in my github repository (https://github.com/abinashi-prakash/ShinyApp).     

## Sachin's Score Snapshot: 
```{r Data_Table,message=FALSE,echo=FALSE,warning=FALSE}
library(dplyr)
library(ggplot2)
Sachin_Data <- read.csv("https://raw.githubusercontent.com/abinashi-prakash/ShinyApp/master/tendulkar.csv",header = TRUE)
##Prepare Data and Calculate the SUM of Runs for each opposton.
Sachin_Runs <- data.frame(format(as.POSIXct(Sachin_Data$Start_Date,format="%d-%m-%Y"),"%Y"),substr(Sachin_Data$Opposition,3,15),as.character(Sachin_Data$Dismissal),Sachin_Data$Runs)
names(Sachin_Runs) <- c("Year", "Opposition", "Dismissal","Runs")
Sachin_Runs <- Sachin_Runs[!(Sachin_Runs$Runs == "" | is.na(Sachin_Runs$Runs) |Sachin_Runs$Runs == "DNB" | Sachin_Runs$Runs == "TDNB"), ]
##Get Run scored against each test playing country
Sachin_Runs <- Sachin_Runs %>% group_by(Opposition) %>% summarise("Runs" = sum(as.numeric(as.character(Runs))))
Sachin_Runs
```